### 2018-07-13 paper/security-discussion.tex
Makes sphinxes branch compile
WIP on Sphinxes
Adds comment to security discussion

>>>>

\commentDaniel{We need to prove that our POR still fulfil the CL definition of 
  OR.
  Since they formalize and idealize ordinary OR we need to see that our changes 
  still work.}

\commentDaniel{Retransmission is not captured in the CL OR-model, that's fine 
  since packets are dropped.
  We must capture the behaviour that if the adversary interrupts transmission, 
  we will try to send to another node.
  We can probably fix this by outputting all nodes in the next layer in the 
  ideal model.}
